Computing astrophysical inferences with diffusive nested sampling

### 2014-01-06 ms.tex
Sentences
Slight edits

A joint prior is assigned on the hypothesis space of possible $\pars$ values
and possible data sets $\data$:
\begin{eqnarray}
p(\pars, \data) = p(\pars) p(\data | \pars) = p(\data)p(\pars | \data)
\end{eqnarray}
The marginal distribution $p(\pars)$, which is usually called the ``prior'',
describes initial uncertainty about the value of the parameters. When the
data $\data$ becomes known, our state of knowledge about $\pars$ changes
from the marginal $p(\pars)$ to the conditional distribution $p(\pars | \data)$
that corresponds to the observed data, usually called the ``posterior''.
Incidentally, Bayesian inference can be understood as a special case of
MaxEnt updating, starting from the joint prior $p(\pars, \data)$ and applying
the constraint $P(\data = \data_{\rm actual}) = 1$ \citep{caticha}. Note that
this is not a ``derivation'' of Bayesian updating as the rules of probability
already imply a commitment to update to $p(\pars | \data)$ once $\data$ becomes
known (what else could a conditional probability be?).

>>>>

In many subfields within astronomy, Bayesian inference has (rightfully)
become the dominant framework for analysing data and quantifying the
plausibility of hypotheses about the universe.

The first step is to construct a set of possible answers to the question of
interest, that is, the ``hypothesis space'', indexed by parameters $\pars$.
A space of possible data sets $\data$ is considered, and a joint prior is
assigned:
\begin{eqnarray}
p(\pars, \data) = p(\pars) p(\data | \pars) = p(\data)p(\pars | \data)
\end{eqnarray}
The marginal distribution $p(\pars)$, which is usually called the ``prior'',
describes initial uncertainty about the value of the parameters. When the
data $\data$ becomes known, our state of knowledge about $\pars$ changes
from the marginal $p(\pars)$ to the conditional distribution $p(\pars | \data)$
that corresponds to the observed data, usually called the ``posterior''.
Incidentally, Bayesian inference can be understood as a special case of
MaxEnt updating, starting from the joint prior $p(\pars, \data)$ and applying
the constraint $P(\data = \data_{\rm actual}) = 1$ \citep{caticha}. Note that
this is not a ``derivation'' of Bayesian updating as the rules of probability
already imply a commitment to update to $p(\pars | \data)$ once $\data$ becomes
known (what else could a conditional probability be?).
